\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/arch.tex
updates to arch and results mostly cosmetic

@@

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can integrate that from
  now there's now way to take water samples. It is still able to
  navigate as \texttt{Pilot} is still available which allow him to
  continue this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

@@

Consider for example the Shopping Agent model where the timeline 
\texttt{Agent.position} is {\em external} while \texttt{Agent} is
implemented a an {\em internal} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.
x1
\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}

>>>>

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can identify that, from
  now on, there's no way to take water samples. It still can 
  navigate as \texttt{Pilot} is available which allow him to continue
  this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

@@

@@

Consider for example the Shopping Agent model where the timeline 
\texttt{Agent.position} is {\em external} while \texttt{Agent} is
implemented a an {\em internal} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.

\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small The Shopping example: Tokens in {\color{red}red}
      indicate observations, tokens in {\color{blue}blue} the goal
      that this plan attempts to solve for. Arrows indicate temporal
      constraints. }
  \label{fig:shop:exec}
\end{figure}

### 2012-02-24 trunk/results.tex
updates to arch and results mostly cosmetic

\begin{figure}[htpb]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows red track lines of the \rx commanded
  Dorado with the yellow transects of the LRAUV. Yellow dots show the
  track line of a simple GPS-enabled drifter used for seeding the
  experiment over the Monterey Canyon with Santa Cruz, CA to the right
  of the figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[The \od Concept]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
\subfloat[Current Implementation for \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with
  the \od in use. Fig. \ref{fig:odss-virtual} shows a drifter tracking
  tool used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. Fig. \ref{fig:odss-ipad} shows \od use on a portable
  iPad device.}
\label{fig:odss2}
\end{figure*}

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of the
  LRAUV. {\color{yellow}Yellow} dots show the track line of a
  GPS-enabled drifter used for seeding the experiment over the
  Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
  \subfloat[Current Implementation for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small \ref{fig:odss-mtg} shows a 2010 \can meeting with the
  \od in use. \ref{fig:odss-virtual} shows a drifter tracking tool
  used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. \ref{fig:odss-ipad} shows \od use on a portable iPad
  device.}
\label{fig:odss2}
\end{figure*}
